---
title: "CCOBRA data set BDA"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r}
knitr::opts_chunk$set(cache = TRUE)
```


```{r}
library(tidyverse)
library(tidyboot)
library(ggplot2)
library(ggthemes)
library(knitr)
library(coda)
library(purrr)
library(dplyr)
library(tidyr)
library(viridis)

library(feather)


theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
HPDhi<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
HPDlo<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

## Load human data

```{r}
# df <- read_csv("ccobra_data/ragni2016_collapse.csv")
df <- read_csv("ccobra_data/ragni2016.csv")


count_summary_fn <- function(x) x %>% 
  summarize(n = n()) %>%
  mutate(stat = n / sum(n))

mean_ci_funs <- list("ci_lower" = ci_lower, "mean" = mean, "ci_upper" = ci_upper)

df %>%
  group_by(premise_1, premise_2, conclusion) %>%
  tidyboot(summary_function = count_summary_fn,
           statistics_functions = function(x) x %>%
             summarise(across(stat, mean_ci_funs, .names = "{.fn}"))) %>%
  ungroup() %>% 
  rowwise() %>%
  mutate(conclusion_quantifier = str_split(conclusion, ";")[[1]][1]) -> df.summ



bind_rows(
  df.summ,
  df %>%
      group_by(premise_1, premise_2, conclusion) %>%
    count() %>% 
    ungroup() %>%
    group_by(premise_1, premise_2) %>%
    mutate(prop = n / sum(n),
           N = sum(n)) %>%
    ungroup() %>%
    select(-n) %>%
    pivot_wider(names_from = conclusion, values_from = prop, values_fill = 0) %>%
    pivot_longer(c(-premise_1, -premise_2, -N), names_to = "conclusion", values_to = "proportion") %>%
    filter(proportion == 0) %>%
    rename(mean = proportion) %>%
    select(-N) %>%
    mutate(n = 0, empirical_n = 0, empirical_stat = 0, ci_lower = 0, ci_upper = 0) %>%
    rowwise() %>%
    mutate(
      conclusion_quantifier = str_split(conclusion, ";")[[1]][1]
    )
) -> df.summ.long.wZeros




  # count() %>% 
  # ungroup() %>%
  # group_by(premise_1, premise_2) %>%
  # count_summary_fn()
  # 
  # mutate(prop = n / sum(n),
  #        N = sum(n)) %>%
  # ungroup() %>%
  # select(-n) %>%
  # pivot_wider(names_from = conclusion, values_from = prop, values_fill = 0) %>%
  # pivot_longer(c(-premise_1, -premise_2, -N), names_to = "conclusion", values_to = "proportion") %>%
  # rowwise() %>%
```


```{r eval = F}
all_workers <- unique(df$id)
n_workers <- length(all_workers)

split_half <- function(){
  sampled_half <- sample(all_workers, size = n_workers/2)

  df %>%
    select(id, premise_1, premise_2, conclusion) %>%
    mutate(split_half = ifelse(id %in% sampled_half, "one", "two")) %>%
    group_by(split_half, premise_1, premise_2, conclusion) %>%
    count() %>% 
    ungroup() %>%
    group_by(split_half, premise_1, premise_2) %>%
    mutate(prop = n / sum(n)) %>%
    select(-n) %>%
    pivot_wider(names_from = split_half, values_from = prop, values_fill = 0) %>%
    ungroup() %>%
    summarize(correlation = cor(one, two, use = "pairwise.complete.obs")) %>%
    pull(correlation)
  
}

split.half.corrs <- replicate(100, split_half())

mean(split.half.corrs)
2* mean(split.half.corrs) / (1 + mean(split.half.corrs))
```


## Load model results

```{r}
model.path <- "results/openmind/refac_runs_feb21/"
# model.prefix <- "results-syllogisms-ragni2016_collapse_"
# model.prefix <- "mll-syllogisms-ragni2016_full_"
model.prefix <- "refac-bda-0paramPrior-syllogisms-ragni2016_full_"

model.names <- c(
  "M00_LIT_LIT", 
  "M01_LIT_PRAG_BELIEF",
  "M02_LIT_PRAG_STATE"#, 
  # "M10_PRAG_STATE_LIT", "M11_PRAG_STATE_PRAG_BELIEF", "M12_PRAG_STATE_PRAG_STATE",
  # "M20_PRAG_QUD_LIT", "M21_PRAG_QUD_PRAG_BELIEF",
  # "M22_PRAG_QUD_PRAG_STATE"
)

m.preds <- data.frame()

m.preds <- map_dfr(model.names, function(model.type){
      
          model.files <- list.files(
            path = model.path,
            # pattern = paste(model.prefix, interpretation, "-interpretation_", 
            #                 production, "-productionKL", sep = "")
            pattern = paste(model.prefix, 
                            model.type,
                            sep = "")
          )
          
          map_dfr(model.files, function(model.file){
           
           read_csv(paste(model.path, model.file, sep = "")) %>%
              mutate(
                model_type = model.type,
                chain = which(model.file == model.files) 
                )
            
      })
  
    })


```


```{r eval= F}
model.types <- c("modular")
# model.types <- c("modular")
interpretation.models <- c("literal")#, "pragmatic")
#interpretation.models <- c("pragmatic")
production.models <- c("literal", "pragmatic")
quds <- c("NA", "state", "AC")#, "seq", "head")
# quds <- c("seq")
alt_utts <- c("NA", "quantifier", "quantifierOrder", "maximal") # "NA")

model.path <- "results/openmind/201211/"
# model.prefix <- "results-syllogisms-ragni2016_collapse_"
model.prefix <- "bda-syllogisms-ragni2016_full_"


m.preds <- map_dfr(model.types, function(model.type){
  map_dfr(interpretation.models, function(interpretation){
    
    map_dfr(production.models, function(production){
      map_dfr(alt_utts, function(alt_utt){
        map_dfr(quds, function(qud){
      
          model.files <- list.files(
            path = model.path,
            # pattern = paste(model.prefix, interpretation, "-interpretation_", 
            #                 production, "-productionKL", sep = "")
            pattern = paste(model.prefix, 
                            model.type, "_",
                            interpretation, "-interpretation_", 
                            production, "-production_",
                            qud, "-qud_",
                            alt_utt, "-alternatives",
                            sep = "")
          )
          
          map_dfr(model.files, function(model.file){
           
           read_csv(paste(model.path, model.file, sep = "")) %>%
              mutate(
                model_type = model.type,
                interpretation = interpretation,
                production = production,
                alt_utt = alt_utt, # ifelse(alt_utt == "", "Q", alt_utt),
                qud = qud,
                chain = which(model.file == model.files) 
                )
            
          })
      
        })
      
      })
      
    })
  })
})
```


```{r}
#path <- "models_10kX3_12072020.feather"
path <- "models_10kX3_0222021.feather"
# write_feather(m.preds, path)
m.preds <- read_feather(path)
```

### Gelman diagnostic

```{r}

# model_name <- "M01_LIT_PRAG_BELIEF"
model_name <- "M02_LIT_PRAG_STATE"
# model_name <- "M00_LIT_LIT"
mh.draws1 <- m.preds %>%
#  filter(chain == 1, model_type == "M00_LIT_LIT") %>%
  filter(chain == 1, model_type == model_name) %>%
  # filter(type == "parameter", premise_1 != "statePrior") %>%
  # filter(type == "prediction") %>%
  select(-chain, -score, -model_type) %>%
  unite("param", c(type, premise_1, premise_2, conclusion)) %>%
  spread(param, val) %>%
   select(-`parameter_nvcWeight_-99_-99`) %>%
  select(-iter) %>% 
  mcmc(.)

mh.draws2 <- m.preds %>%
  #filter(chain == 2, model_type == "M00_LIT_LIT") %>%
  filter(chain == 2, model_type == model_name) %>%
  # filter(type == "parameter", premise_1 != "statePrior") %>%
  # filter(type == "prediction") %>%
  select(-chain, -score, -model_type) %>%
  unite("param", c(type, premise_1, premise_2, conclusion)) %>%
  spread(param, val) %>%
  select(-`parameter_nvcWeight_-99_-99`) %>%
  select(-iter) %>% 
  mcmc(.)

mh.draws3 <- m.preds %>%
  # filter(chain == 3, model_type == "M00_LIT_LIT") %>%
  filter(chain == 3, model_type == model_name) %>%
  # filter(type == "parameter", premise_1 != "statePrior") %>%
  # filter(type == "prediction") %>%
  select(-chain, -score, -model_type) %>%
  unite("param", c(type, premise_1, premise_2, conclusion)) %>%
  spread(param, val) %>%
  select(-`parameter_nvcWeight_-99_-99`) %>%
  select(-iter) %>% 
  mcmc(.)


mh.list <- coda::mcmc.list(
  list(mh.draws1, mh.draws2, mh.draws3)
  )

rhat.rs <- gelman.diag(mh.list, multivariate = FALSE)
df.rhat <- data.frame(rhat.rs$psrf)

summary(df.rhat$Point.est.)

head(df.rhat, 11)
```


## Parameters

### Global Parameters

```{r fig.width = 8}
m.preds %>% 
  filter(type == "parameter", premise_1 != "statePrior") %>%
  # filter(model_type == "M01_LIT_PRAG_BELIEF") %>%
  filter(val != -99) %>% 
  unite(param, c(premise_1, premise_2)) %>%
  # unite(model, c(model_type, interpretation, production, qud, alt_utt )) %>%
  mutate(chain = factor(chain)) %>%
  ggplot(., aes( x = val, fill = chain))+
  geom_histogram(position = position_dodge())+
  facet_grid(model_type ~param, scales = 'free')+
  theme(strip.text.y =  element_text(angle = 0))

# ggsave("../analysis/figs/bda_ragni_params_byChain_0params.pdf", width = 12, height = 5)

```



```{r fig.width=12}
m.preds %>% 
  filter(type == "parameter", premise_1 != "statePrior") %>%
  filter(val != -99) %>% 
  # unite(param, c(premise_1, premise_2)) %>%
  unite(param, c(premise_1)) %>%
  # unite(model, c(model_type, interpretation, production, qud, alt_utt)) %>%
  group_by(model_type, param) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = HPDhi(val),
            cred_lower = HPDlo(val)) -> m.params.summary

ggplot(m.params.summary, aes( x = model_type, y = MAP, ymin = cred_lower,
                                    ymax = cred_upper, fill = model_type))+
  geom_col(position = position_dodge())+
  geom_linerange(position = position_dodge())+
  facet_wrap(~param, scales  = 'free') +
  coord_flip()+
  guides(fill = F)
  # theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

m.params.summary %>% kable()

```

Write out to .csv

```{r}
m.params.summary %>%
  mutate(paramEst = paste(
    round(MAP, 2), " (", round(cred_lower, 2), ", ", round(cred_upper, 2), ")",
    sep = ""
  )) %>%
  unite(model_param, c("model_type", "param")) %>%
  write_csv(.,
          file = "../publications/topics/csv_to_tex/rsa_model_params_0param.csv")
```




### State priors 

```{r fig.width=14}
m.preds %>% 
    # filter( (model_type == "M00_LIT_LIT" & chain %in% c(1)  ) |
    #       (model_type == "M01_LIT_PRAG_BELIEF" & chain %in% c(2, 3)) |
    #       (model_type == "M02_LIT_PRAG_STATE" & chain %in% c(3)  )) %>%
  filter(type == "parameter", premise_1 == "statePrior") %>%
  mutate(
    premise_2 = ifelse(is.na(premise_2), "empty", premise_2),
    region = factor(premise_2, levels = 
                              c("empty", "A", "B", "C", "AB", "BC", "AC", "ABC")),
    chain = factor(chain)) %>%
  # filter(val != -99) %>% 
  # unite(param, c(premise_1, premise_2)) %>%
  # unite(model, c(model_type, interpretation, production, qud, alt_utt)) %>%
  unite(model, c(model_type)) %>%
  ggplot(., aes( x = val, fill = chain))+
  geom_histogram(position = position_dodge())+
  facet_grid(model+ chain~region, scales = 'free')+
  scale_x_continuous(limits = c(0, 1))+
  theme(strip.text.y =  element_text(angle = 0))

# ggsave("../analysis/figs/bda_ragni_stateParams2_byChain_02222021.pdf", width = 16, height = 20)

```

Summary of State Priors Parameters
```{r fig.width = 7}
m.preds %>% 
    filter( (model_type == "M00_LIT_LIT" & chain %in% c(1)  ) |
          (model_type == "M01_LIT_PRAG_BELIEF" & chain %in% c(2, 3)) |
          (model_type == "M02_LIT_PRAG_STATE" & chain %in% c(3)  )) %>%
  filter(type == "parameter", premise_1 == "statePrior") %>%
  mutate(premise_2 = ifelse(is.na(premise_2), "empty", premise_2),
    region = factor(premise_2, levels = 
                              c("empty", "A", "B", "C", "AB", "BC", "AC", "ABC")),
    chain = factor(chain)) %>%
  #unite(model, c(model_type, interpretation, production, qud, alt_utt)) %>%
  unite(model, c(model_type)) %>%
  group_by(model, region) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = HPDhi(val),
            cred_lower = HPDlo(val)) -> m.state.priors.summary

ggplot(m.state.priors.summary, aes( x = region, y = MAP, ymin = cred_lower,
                                    ymax = cred_upper))+
  geom_col(position = position_dodge())+
  geom_linerange(position = position_dodge())+
  facet_wrap(~model, nrow = 3)

m.state.priors.summary
```



## Posterior predictions


```{r}


m.summary <- m.preds %>%
  filter(type == "prediction") %>%
    # filter( (model_type == "M00_LIT_LIT" & chain %in% c(1)  ) | # for 2 param model
    #       (model_type == "M01_LIT_PRAG_BELIEF" & chain %in% c(2, 3)) |
    #       (model_type == "M02_LIT_PRAG_STATE" & chain %in% c(3)  )) %>%  
  # filter(!(chain == 4 & model_type == "modular" & interpretation == "pragmatic" & 
   #           production == "pragmatic" & qud == "seq" & alt_utt == "Q")) %>%
  #rename(premise_1 = param, premise_2 = property, conclusion = category) %>%
  #group_by(model_type, interpretation, production, qud, alt_utt, premise_1, premise_2, conclusion) %>%
    group_by(model_type, premise_1, premise_2, conclusion) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = HPDhi(val),
            cred_lower = HPDlo(val))

# write_csv(m.summary, "models_10kX3_11092020_summary.csv")
```

```{r fig.width = 6}
md.summary <- left_join(m.summary, df.summ.long.wZeros)  %>%
  #unite(model, c(model_type, interpretation, production, qud, alt_utt))
  unite(model, c(model_type))

# write_csv(md.summary, "../publications/topics/cached_results/md_summary_0paramPrior.csv")

md.summary <- read_csv("../publications/topics/cached_results/md_summary_0paramPrior.csv")

md.summary %>%
    mutate(model = factor(model,
                        levels = c("M00_LIT_LIT", "M02_LIT_PRAG_STATE",
                                   "M01_LIT_PRAG_BELIEF"),
                        labels = c("Literal Speaker",
                                   "State Communication\n(Pragmatic Speaker)",
                                   "Belief Alignment\n(Pragmatic Speaker)")),
         conclusion_quantifier = factor(conclusion_quantifier,
                                        levels = c("All", "Some", "Some not", "No", "NVC"),
                                        labels = c("All", "Some", "Some...not", "None",
                                                   "nothing follows"))) %>%
  ggplot(., aes( x = MAP, y = mean, 
                 fill = conclusion_quantifier,
                 xmin = cred_lower, xmax = cred_upper,
                 ymin = ci_lower, ymax = ci_upper))+
  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = 0.3)+
  geom_linerange(alpha = 0.4)+
  ggstance::geom_linerangeh( alpha = 0.4 )+
  geom_point(shape = 21, size = 1.5)+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  # facet_grid(interpretation ~ production)+
  guides(fill = guide_legend(title = "Conclusion\nQuantifier"))+
  facet_wrap( ~ model, nrow = 1)+
  coord_fixed(ratio = 1)+
  labs(
    x = "Model Prediction",
    y = "Human Conclusions\n(proportion)"
  )

  # ggplot(., aes( x = model_mean, xmin = model_lower, xmax = model_upper, 
  #                fill = conclusion_quantifier,
  #                y = mean, ymin = ci_lower, ymax = ci_upper))+
  # geom_abline(intercept = 0, slope = 1, lty = 3, alpha = 0.3)+
  # geom_linerange(alpha = 0.4)+
  # ggstance::geom_linerangeh( alpha = 0.4 )+
  # geom_point(shape = 21, size = 1.5)+
  # scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  # scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  # #xlim(0, 1) + ylim(0, 1)+
  # coord_fixed()+
  # guides(fill = guide_legend(title = "Conclusion quantifier"))+
  # #scale_fill
  # #scale_fill_viridis(discrete = T, option = "E")+
  # facet_wrap(~model, nrow = 1)+
  # labs(
  #   x = "Model Prediction (mean)",
  #   y = "Human Conclusions\n(proportion)"
  # )




# ggsave("../publications/topics/figs/bda_rsa_scatters_0paramPrior.pdf", width = 9.2, height = 3.2)


  # ggsave("../analysis/figs/bda_ragni_scatters_02222021a.pdf", width = 12, height = 8)

```

```{r}
md.summary %>%
  group_by(model) %>%
  summarize(
    r = cor(MAP, mean),
    r2 = r^2,
    mse = mean((MAP-mean) ^2 )
  ) %>%
  kable(.)
```

### Full posterior distribution for predictions

```{r}
m.preds %>%
  filter(type == "prediction", model_type == "M01_LIT_PRAG_BELIEF") %>%
  filter(premise_1 %in% c("No;A;B", "All;A;B", "Some not;A;B", "Some;A;B"),
         premise_2 %in% c("No;B;C", "All;B;C", "Some not;B;C", "Some;B;C")) -> m.preds.filtered

m.preds.filtered %>%
  ggplot(., aes( x = val, fill = conclusion))+
  geom_histogram(color = 'black')+
  facet_grid(premise_1 + premise_2 ~ conclusion, scales = 'free')+
  scale_fill_viridis(discrete = T)
  
ggsave("../analysis/figs/bda_ragni_postPred_histograms.pdf", width = 20, height = 12)

```


### NVC

```{r fig.width = 6}
md.summary  %>%
  filter(conclusion_quantifier == "NVC") %>%
  mutate(model = factor(model,
                        levels = c("M00_LIT_LIT", "M02_LIT_PRAG_STATE",
                                   "M01_LIT_PRAG_BELIEF"),
                        labels = c("Literal Speaker",
                                   "State Communication\n(Pragmatic Speaker)",
                                   "Belief Alignment\n(Pragmatic Speaker)"))) %>%
  ggplot(., aes( x = MAP, y = mean,
                 xmin = cred_lower, xmax = cred_upper,
                 ymin = ci_lower, ymax=ci_upper))+
  geom_point()+
  ggstance::geom_linerangeh()+
  geom_linerange(alpha = 0.4)+
  facet_wrap( ~ model, nrow = 1)+
  coord_fixed(ratio = 1)+
  geom_point(shape = 21, size = 1.5)+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  xlab('Model Prediction\n ("Nothing Follows")')+
  ylab('Human Proportion\n ("Nothing Follows")')

ggsave("../publications/topics/figs/bda_rsa_scatters_0paramPrior_nvc.pdf", width = 6.5, height = 3)
```

```{r}
md.summary  %>%
  filter(conclusion_quantifier == "NVC") %>%
  group_by(model) %>%
  summarize(
    r = cor(MAP, mean),
    r2 = r^2,
    mse = mean((MAP-mean) ^2 )
  ) %>%
  kable(.)
```



```{r}
best.models <- c(
  "modular_pragmatic_literal_seq_quantifier",
  "modular_pragmatic_pragmatic_AC_quantifier",
  "modular_pragmatic_pragmatic_seq_quantifier",
  "modular_pragmatic_pragmatic_state_quantifier"
)
```




### **Quantifier choice**

model-fit by conclusion quantifier


```{r fig.width = 12}
md.summary %>%
  filter(model %in% best.models) %>%
  ggplot(., aes( x = MAP, y = proportion, color = conclusion_quantifier,
                 xmin = cred_lower, xmax = cred_upper))+
  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = 0.3)+
  geom_point()+
  ggstance::geom_linerangeh(alpha = 0.3)+
  facet_grid(model ~ conclusion_quantifier)+
  coord_fixed(ratio = 1)+
  theme(strip.text.y = element_text(angle = 0))+
  xlim(0, 1)+
  ylim(0, 1)
```



### **Term order**

how often does the model pick "A-C" vs. "C-A" (in comparison to people)




## Residuals analysis

```{r, eval = F}

best.models <- c(
  #"integrated_pragmatic_literal_grounded_Q",
  "M00_LIT_LIT",
  "M01_LIT_PRAG_BELIEF",
  "M02_LIT_PRAG_STATE"
)

# Compute Sum Sq Err for each syllogism/model
md.summary %>% 
  filter(model == "M01_LIT_PRAG_BELIEF") %>%
  group_by(model, premise_1, premise_2) %>%
  summarize(sum_sq_err = sum((MAP - mean)^2)) %>%
  ungroup() %>%
  unite(syllogism, c(premise_1, premise_2)) -> md.err


# Select top/bottom error 10 syllogisms 
bind_rows(
  md.err[with(md.err, order(-sum_sq_err)), ] %>%
    head(10),
  md.err[with(md.err, order(-sum_sq_err)), ] %>%
    tail(10)
) %>%
  distinct(syllogism) %>%
  pull(syllogism) -> best.worst.syllogisms

# bottom 10 only...
md.err[with(md.err, order(-sum_sq_err)), ] %>%
  head(10) %>%
  distinct(syllogism) %>%
  pull(syllogism) -> worst.syllogisms


# bottom 10 only...
md.err[with(md.err, order(-sum_sq_err)), ] %>%
  tail(10) %>%
  distinct(syllogism) %>%
  pull(syllogism) -> best.syllogisms

# subset data frame to only top/bottom syllogisms

md.summary %>% 
  filter(model %in% best.models) %>%
  unite(syllogism, c(premise_1, premise_2)) -> md.summary.residuals # %>%
  # filter(syllogism %in% best.worst.syllogisms) 

# turn data frame into long form for bar plots
bind_rows(
  md.summary.residuals %>%
    select(-mean, -ci_lower, -ci_upper, -empirical_n, -empirical_stat),
  md.summary.residuals %>%
    select(-MAP, -cred_upper, -cred_lower) %>%
    rename(MAP = mean,
           cred_upper = ci_upper,
           cred_lower = ci_lower) %>%
    select(-model, -empirical_n, -n) %>%
    distinct(syllogism, conclusion, MAP, cred_upper, cred_lower, conclusion_quantifier) %>%
    mutate(model = "data")
) -> md.summary.residuals.long


# left_join(
#   md.summary.residuals.long,
#   md.err
# ) 
md.summary.residuals.long %>%
  filter(syllogism %in% best.syllogisms) %>%
  mutate(conclusion = factor(conclusion, levels = c(
      "All;A;C","All;C;A", "Some;A;C", "Some;C;A", "Some not;A;C", "Some not;C;A", "No;A;C", "No;C;A", "NVC;"
    ))) %>%
  ggplot(., aes ( x = model, y = MAP, ymin = cred_upper, ymax = cred_upper,
                fill = conclusion))+
  geom_col(position = position_dodge(), color = 'black')+
  geom_linerange(position = position_dodge())+
  scale_fill_viridis(discrete = T)+
  facet_wrap(~syllogism, nrow = 2)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

# ggsave("../analysis/figs/bda_ragni_litPrag_v_pragPrag_bestFitSyll_12142020.pdf", width = 14, height = 6)

md.summary.residuals.long %>%
  filter(syllogism %in% worst.syllogisms) %>%
  mutate(conclusion = factor(conclusion, levels = c(
      "All;A;C","All;C;A", "Some;A;C", "Some;C;A", "Some not;A;C", "Some not;C;A", "No;A;C", "No;C;A", "NVC;"
    ))) %>%
  ggplot(., aes ( x = model, y = MAP, ymin = cred_upper, ymax = cred_upper,
                fill = conclusion))+
  geom_col(position = position_dodge(), color = 'black')+
  geom_linerange(position = position_dodge())+
  scale_fill_viridis(discrete = T)+
  facet_wrap(~syllogism, nrow = 2)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

# ggsave("../analysis/figs/bda_ragni_litPrag_v_pragPrag_worstFitSyll_12142020.pdf", 
#        width = 14, height = 6)
```

Residuals for NVC

```{r}
# Compute Sum Sq Err for each syllogism/model
md.summary %>% 
  filter(model == "M01_LIT_PRAG_BELIEF", conclusion_quantifier == "NVC") %>%
  group_by(model, premise_1, premise_2) %>%
  summarize(sum_sq_err = (MAP - mean)^2) %>%
  ungroup() %>%
  unite(syllogism, c(premise_1, premise_2)) -> md.err.nvc

# bottom 10 only...
md.err.nvc[with(md.err.nvc, order(-sum_sq_err)), ] %>%
  head(10) %>%
  distinct(syllogism) %>%
  pull(syllogism) -> worst.nvc.syllogisms


# top 10 only...
md.err.nvc[with(md.err.nvc, order(-sum_sq_err)), ] %>%
  tail(10) %>%
  distinct(syllogism) %>%
  pull(syllogism) -> best.nvc.syllogisms

```






## Bar plots

```{r}
md.summary.residuals.long %>%
  ungroup() %>%
  separate(syllogism, into= c("premise_1", "premise_2", "to1b"), "_") %>%
  separate(premise_1, into= c("quant1", "to1a", "to1b"), ";") %>%
  separate(premise_2, into= c("quant2", "to2a", "to2b"), ";") %>%
  unite(to1, c("to1a", "to1b"), sep = "") %>%
  unite(to2, c("to2a", "to2b"), sep = "") %>%
  filter(to1 == "AB", to2 == "BC") %>%
  unite(syllogism, c(quant1, quant2), sep = " / ") %>%
  mutate(model = factor(model, levels = c( "data", "M01_LIT_PRAG_BELIEF",
                                             "M02_LIT_PRAG_STATE", "M00_LIT_LIT"),
                          labels = c("Human Data",
                                   "Belief Alignment",
                                   "State Communication","Literal Speaker")),
      Conclusion = factor(conclusion, 
                          levels = c("All;A;C","All;C;A", 
                                     "Some;A;C", "Some;C;A", 
                                     "Some not;A;C", "Some not;C;A", 
                                     "No;A;C", "No;C;A", "NVC;"),
                          labels = c("All A are C", "All C are A",
                                     "Some A are C", "Some C are A",
                                     "Some A are not C", "Some C are not A",
                                     "No A are C", "No C are A",
                                     "Nothing follows")
    )) -> md.summary.residuals.long.bars


bar.width = 0.8
ggplot(md.summary.residuals.long.bars, aes ( x = model, y = MAP, 
                                             ymin = cred_lower, ymax = cred_upper,
                fill = Conclusion))+
  geom_col(position = position_dodge(bar.width), width = bar.width, color = 'black',
           alpha = 0.8)+
  geom_linerange(position = position_dodge(bar.width))+
  scale_fill_viridis(discrete = T)+
  facet_wrap(~syllogism, nrow = 4)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  labs(
    y = "Predicted probability / Empirical proportion",
    x = ""
  )

ggsave("../publications/topics/figs/bda_rsa_bars_0params.pdf", width = 11, height = 7)

```



Examination of "nothing follows"

```{r}
d.summary.human.bars.nvc <- md.summary.residuals.long.bars  %>%
  filter(Conclusion == "Nothing follows", model == "Belief Alignment")

md.summary.residuals.long.bars %>%
  filter(Conclusion == "Nothing follows") %>%
  mutate(syllogism = factor(syllogism,
                             levels = with(d.summary.human.bars.nvc,
                                           syllogism[order(-MAP)]))) %>%
  ggplot(., aes ( x = syllogism, y = MAP, ymin = cred_lower, ymax = cred_upper,
                fill = model))+
  geom_col(position = position_dodge(bar.width), 
           width = bar.width, 
           color = 'black',
           alpha = 0.8)+
  geom_linerange(position = position_dodge(bar.width))+
  scale_fill_viridis(discrete = T)+
  facet_wrap(~model, nrow = 1)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  labs(
    y = "Predicted probability / Empirical proportion",
    x = ""
  )
```




```{r}
# Compute Sum Sq Err for each syllogism/model
md.summary %>% 
  filter(model %in% c("M00_LIT_LIT",
  "M01_LIT_PRAG_BELIEF")) %>%
  group_by(model, premise_1, premise_2) %>%
  summarize(sum_sq_err = sum((MAP - mean)^2)) %>%
  ungroup() %>%
  unite(syllogism, c(premise_1, premise_2)) -> md.err.m

md.err.m %>%
  pivot_wider(names_from = model, values_from = sum_sq_err) %>%
  rowwise() %>%
  mutate(lit_minus_belief = M00_LIT_LIT - 
           M01_LIT_PRAG_BELIEF) %>% View()
```

KL Divergence

```{r}

md.summary %>%
  group_by(model, premise_1, premise_2, conclusion) %>%
  mutate(div = ifelse( mean == 0, 0, mean * log( mean / MAP))) %>%
  group_by(model, premise_1, premise_2) %>%
  summarize(
    KL = sum(div)
    ) -> md.kl


md.summary %>%
  filter(model %in% c("M00_LIT_LIT",
  "M01_LIT_PRAG_BELIEF"#,
    #"modular_pragmatic_pragmatic_state_quantifier"
    )) %>%
    group_by(model, premise_1, premise_2) %>%
  summarize(sum_sq_err = sum((MAP - mean)^2)) %>%
  ungroup() %>%
  unite(syllogism, c(premise_1, premise_2)) %>%
  pivot_wider(names_from = model, values_from = sum_sq_err) %>%
  mutate(dev_err = M00_LIT_LIT - 
           M01_LIT_PRAG_BELIEF) -> md.err.model.wide

md.kl %>%
  ggplot(., aes ( x = KL ))+
  geom_histogram()+
  facet_wrap(~model)

md.kl %>%
  filter(model %in% c(
    "M00_LIT_LIT",
    "M01_LIT_PRAG_BELIEF"#,
    #"modular_pragmatic_pragmatic_state_quantifier"
    )) %>%
  pivot_wider(names_from = model, values_from = KL) %>%
  mutate(dev_KL = M00_LIT_LIT - 
           M01_LIT_PRAG_BELIEF)  -> md.kl.model.wide

# find syllogisms for which AC model fits better than state model
# md.kl.model.wide %>%
#   mutate(dev_KL = modular_literal_pragmatic_state_NA - 
#            modular_pragmatic_pragmatic_AC_quantifier) %>%
#   # mutate(dev_KL = modular_pragmatic_pragmatic_state_quantifier - 
#   #          modular_pragmatic_pragmatic_AC_quantifier) %>%
#   View()
  
md.kl.model.wide %>%
  ggplot(., aes(x = M01_LIT_PRAG_BELIEF, 
                y = M00_LIT_LIT))+
  geom_point()+
  coord_fixed()+
  xlim(0, 1)+
  ylim(0, 1)+
  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = 0.3)
    
```

Cases where Pragmatic Interpretation model does better than Literal Interpretation

```{r}
md.kl.model.wide[with(md.kl.model.wide, order(-dev_KL)), ] %>%
  unite(syllogism, c(premise_1, premise_2)) %>%
  head(10) %>%
  distinct(syllogism) %>%
  pull(syllogism) -> max.dev.syll

md.err.model.wide[with(md.err.model.wide, order(-dev_err)), ] %>%
  head(10) %>%
  distinct(syllogism) %>%
  pull(syllogism) -> max.dev.err.syll

md.summary.residuals.long %>%
  filter(syllogism %in% max.dev.err.syll) %>%
  mutate(conclusion = factor(conclusion, levels = c(
      "All;A;C","All;C;A", "Some;A;C", "Some;C;A", "Some not;A;C", 
      "Some not;C;A", "No;A;C", "No;C;A", "NVC;"
    )),
    syllogism = factor(syllogism, levels = max.dev.err.syll)) %>%
  ggplot(., aes ( x = model, y = MAP, ymin = cred_upper, ymax = cred_upper,
                fill = conclusion))+
  geom_col(position = position_dodge(), color = 'black')+
  geom_linerange(position = position_dodge())+
  scale_fill_viridis(discrete = T)+
  facet_wrap(~syllogism, nrow = 2)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

  ggsave("../analysis/figs/bda_ragni_maxDevErr_litPrag_v_pragPrag_worstFitSyll_12142020.pdf", 
       width = 14, height = 6)
```


Cases where Literal Interpretation model does better than Pragmatic Interpretation

```{r}
md.kl.model.wide[with(md.kl.model.wide, order(dev_KL)), ] %>%
  unite(syllogism, c(premise_1, premise_2)) %>%
  head(10) %>%
  distinct(syllogism) %>%
  pull(syllogism) -> min.dev.syll

md.err.model.wide[with(md.err.model.wide, order(dev_err)), ] %>%
  head(10) %>%
  distinct(syllogism) %>%
  pull(syllogism) -> min.dev.err.syll

md.summary.residuals.long %>%
  filter(syllogism %in% min.dev.syll) %>%
  mutate(conclusion = factor(conclusion, levels = c(
      "All;A;C","All;C;A", "Some;A;C", "Some;C;A", "Some not;A;C", "Some not;C;A", "No;A;C", "No;C;A", "NVC;"
    )),
    syllogism = factor(syllogism, levels = min.dev.syll)) %>%
  ggplot(., aes ( x = model, y = MAP, ymin = cred_upper, ymax = cred_upper,
                fill = conclusion))+
  geom_col(position = position_dodge(), color = 'black')+
  geom_linerange(position = position_dodge())+
  scale_fill_viridis(discrete = T)+
  facet_wrap(~syllogism, nrow = 2)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

ggsave("../analysis/figs/bda_ragni_minDev_litPrag_v_pragPrag_worstFitSyll_12142020.pdf", 
       width = 14, height = 6)
```


Cases where literal interpretation is most different from pragmatic interpretation

```{r}
md.summary %>%
  filter(model %in% c(
    "modular_literal_pragmatic_state_NA",
    "modular_pragmatic_pragmatic_AC_quantifier"#,
    #"modular_pragmatic_pragmatic_state_quantifier"
    )) %>%
  select(model, premise_1, premise_2, conclusion, MAP) %>%
  pivot_wider(names_from = model, values_from = MAP) %>%
  group_by(premise_1, premise_2) %>%
  summarize(sum_sq_err = sum( (modular_literal_pragmatic_state_NA - modular_pragmatic_pragmatic_AC_quantifier) ^2 )) %>%
  ungroup() %>%
  unite(syllogism, c(premise_1, premise_2)) -> m.dev.lit.prag

m.dev.lit.prag[with(m.dev.lit.prag, order(-sum_sq_err)), ] %>%
  head(10) %>%
  distinct(syllogism) %>%
  pull(syllogism) -> max.dev.models.syll

md.summary.residuals.long %>%
  filter(syllogism %in% max.dev.models.syll) %>%
  mutate(conclusion = factor(conclusion, levels = c(
      "All;A;C","All;C;A", "Some;A;C", "Some;C;A", "Some not;A;C", "Some not;C;A", "No;A;C", "No;C;A", "NVC;"
    )),
    syllogism = factor(syllogism, levels = max.dev.models.syll)) %>%
  ggplot(., aes ( x = model, y = MAP, ymin = cred_upper, ymax = cred_upper,
                fill = conclusion))+
  geom_col(position = position_dodge(), color = 'black')+
  geom_linerange(position = position_dodge())+
  scale_fill_viridis(discrete = T)+
  facet_wrap(~syllogism, nrow = 2)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

ggsave("../analysis/figs/bda_ragni_maxDevModels_litPrag_v_pragPrag_12152020.pdf", 
       width = 14, height = 6)
```


## Full bar plots

```{r fig.width = 20, eval = F}
# turn data frame into long form for bar plots
bind_rows(
  md.summary %>%
    select(-N, -proportion),
  md.summary %>%
    mutate(MAP = proportion,
           cred_upper = proportion,
           cred_lower = proportion) %>%
    select(-model, -proportion, -N) %>%
    distinct(premise_1, premise_2, conclusion, MAP, cred_upper, cred_lower, conclusion_quantifier) %>%
    mutate(model = "data")
) -> md.summary.long


md.summary.long %>%
  filter(model %in% c(best.models, "data")) %>%
  mutate(
    conclusion = factor(conclusion, levels = c(
      "All;A;C","All;C;A", "Some;A;C", "Some;C;A", "Some not;A;C", "Some not;C;A", "No;A;C", "No;C;A", "NVC;"
    )),
    premise_1 = factor(premise_1, levels = c("All;A;B",
                                             "All;B;A", 
                                             "Some;A;B", "Some;B;A", 
                                             "Some not;A;B", "Some not;B;A", 
                                             "No;A;B", "No;B;A")),
    premise_2 = factor(premise_2, levels = c("All;B;C",
                                             "All;C;B", 
                                             "Some;B;C", "Some;C;B", 
                                             "Some not;B;C", "Some not;C;B", 
                                             "No;B;C", "No;C;B")),
  ) %>%
  ggplot(., aes ( x = model, y = MAP, 
                fill = conclusion, group = conclusion))+
  geom_col(position = position_dodge(), color = 'black')+
  # geom_errorbar(position = position_dodge(),
  #               aes(ymin = cred_upper, ymax = cred_upper))+
  scale_fill_viridis(discrete = T)+
  facet_grid(premise_2~premise_1)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

ggsave("../analysis/figs/bda_ragni_4models_bars_11092020.pdf", width = 20, height = 12)
```



# Model Comparison

## Load model results

```{r}
# model.types <- c("modular")
# # model.types <- c("modular")
# interpretation.models <- c("literal", "pragmatic")
# #interpretation.models <- c("pragmatic")
# production.models <- c("literal", "pragmatic", "litWSoftmax", "state")
# quds <- c("NA", "state", "AC")#, "seq", "head")
# # quds <- c("seq")
# alt_utts <- c("NA", "quantifier")#, "quantifierOrder", "maximal", "NA")

model.path <- "results/mll/"
# model.prefix <- "results-syllogisms-ragni2016_collapse_"
# model.prefix <- "mll-syllogisms-ragni2016_full_"


prior.param <- c("0paramPrior-"
                 # "1paramPrior-",
                 # "2paramPrior-",
                 # "4paramPrior-", 
                 # ""
                 )

#model.prefix <- "refac-ais-syllogisms-ragni2016_full_"
model.prefix <- "refac-ais-"
#"-syllogisms-ragni2016_full_"

model.names <- c(
  "M00_LIT_LIT", "M01_LIT_PRAG_BELIEF",
  "M02_LIT_PRAG_STATE"#, 
  # "M10_PRAG_STATE_LIT",
  # "M11_PRAG_STATE_PRAG_BELIEF", "M12_PRAG_STATE_PRAG_STATE",
  # "M20_PRAG_QUD_LIT", "M21_PRAG_QUD_PRAG_BELIEF",
  # "M22_PRAG_QUD_PRAG_STATE"
)

m.mll <- map_dfr(model.names, function(model.type){
    map_dfr(prior.param, function(priorParam){
        model.files <- list.files(
            path = model.path,
            pattern = paste(model.prefix, priorParam, 
                            "syllogisms-ragni2016_full_",
                            model.type, "_5000",
                            sep = "")
          )
          
          map_dfr(model.files, function(model.file){
           
           read_csv(paste(model.path, model.file, sep = ""),
                    col_types =  cols(
                              modelName = col_character(),
                              steps = col_character(),
                              iter = col_character(),
                              weight = col_character()
                            )) %>%
              mutate(
                model_type = model.type,
                prior_type = ifelse(priorParam == "", 
                                    "7paramPrior", priorParam),
                chain = which(model.file == model.files) 
                )
            
          })
    })
})


m.mll <- m.mll %>%
  mutate_at(vars(steps, iter, weight, chain), as.numeric)
# 
# m.mll <- map_dfr(model.types, function(model.type){
#   map_dfr(interpretation.models, function(interpretation){
#     
#     map_dfr(production.models, function(production){
#       map_dfr(alt_utts, function(alt_utt){
#         map_dfr(quds, function(qud){
#       
#           model.files <- list.files(
#             path = model.path,
#             # pattern = paste(model.prefix, interpretation, "-interpretation_", 
#             #                 production, "-productionKL", sep = "")
#             pattern = paste(model.prefix, 
#                             model.type, "_",
#                             interpretation, "-interpretation_", 
#                             production, "-production_",
#                             qud, "-qud_",
#                             alt_utt, "-alternatives",
#                             sep = "")
#           )
#           
#           map_dfr(model.files, function(model.file){
#            
#            read_csv(paste(model.path, model.file, sep = "")) %>%
#               mutate(
#                 model_type = model.type,
#                 interpretation = interpretation,
#                 production = production,
#                 alt_utt = alt_utt, # ifelse(alt_utt == "", "Q", alt_utt),
#                 qud = qud,
#                 chain = which(model.file == model.files) 
#                 )
#             
#           })
#       
#         })
#       
#       })
#       
#     })
#   })
# })
```


```{r}
m.mll %>%
  # unite("model", c(interpretation, production, qud, alt_utt, alternatives)) %>%
  ggplot(., aes(x = weight, fill = modelName))+
  geom_histogram(position = position_dodge())+
  facet_grid(prior_type~modelName, scale = 'free')+
  theme(strip.text.y = element_text(angle = 0))
```

```{r}
m.mll %>%
  # unite("model", c(interpretation, production, qud, alt_utt, alternatives)) %>%
  group_by(modelName, prior_type, steps) %>%
  summarize(n = n(),
            mll = mean(weight),
          min_mll = min(weight),
          max_mll = max(weight),
        range_mll = min_mll - max_mll
            ) -> m.mll.summary
```
```{r}
m.mll %>%
  filter(steps == 5000) %>%
  unite("model", c(interpretation, production, qud, alt_utt, alternatives)) %>%
  ggplot(., aes(x = weight, fill = model))+
  geom_histogram(position = position_dodge())+
  facet_grid(.~ steps)
```


#### _depracated: Quantifier choice

how often does the model pick "some" vs. "all" (in comparison to people)

```{r}

left_join(
  m.preds %>%
    filter(type == "prediction"),
  m.preds %>%
    filter(type == "prediction") %>% distinct(conclusion) %>%
    rowwise() %>% 
    mutate(conclusion_quantifier = str_split(conclusion, ";")[[1]][1])
) %>%
  group_by(model_type, interpretation, production, qud, alt_utt, premise_1, premise_2, conclusion_quantifier) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = HPDhi(val),
            cred_lower = HPDlo(val)) -> m.summary.quantifier

df %>%
  rowwise() %>%
  mutate(conclusion_quantifier = str_split(conclusion, ";")[[1]][1]) %>%
  group_by(premise_1, premise_2, conclusion_quantifier) %>%
  count() %>% 
  ungroup() %>%
  group_by(premise_1, premise_2) %>%
  mutate(prop = n / sum(n),
         N = sum(n)) %>%
  ungroup() %>%
  select(-n) %>%
  pivot_wider(names_from = conclusion_quantifier, values_from = prop, values_fill = 0) %>%
  pivot_longer(c(-premise_1, -premise_2, -N), names_to = "conclusion_quantifier", values_to = "proportion") -> df.summ.quantifier


```

```{r fig.width = 6}
md.summary.quantifier <- left_join(m.summary.quantifier, df.summ.quantifier)  %>%
  unite(model, c(model_type, interpretation, production, qud, alt_utt))

md.summary.quantifier %>%
  ggplot(., aes( x = MAP, y = proportion, color = conclusion_quantifier,
                 xmin = cred_lower, xmax = cred_upper))+
  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = 0.3)+
  geom_point()+
  ggstance::geom_linerangeh(alpha = 0.3)+
  # facet_grid(interpretation ~ production)+
  facet_wrap( ~ model, nrow = 3)+
  coord_fixed(ratio = 1)+
  xlim(0, 1)+
  ylim(0, 1)
```
