---
title: "Visualizations of sets of venn diagrams (Figs 3-5)"
author: "MH Tessler"
date: "10/29/2020"
output: pdf_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(ggVennDiagram)
library(gridExtra)
library(cowplot)
set.seed(20201027)
```


# Helper function to make Venn Diagram from data frame

```{r}
genes <- paste("sample",1:100000,sep="")

venn_diagram_from_df <- function(df){

  get_venn_samples <- function(df_samples){

    make_venn_sample <- function(region, i){
      samp = genes[i]
      A = ifelse(str_detect(region, "A"), samp, NA)
      B = ifelse(str_detect(region, "B"), samp, NA)
      C = ifelse(str_detect(region, "C"), samp, NA)
       return(data.frame(A = A, B = B, C = C))
    }

    x <- imap(df_samples, make_venn_sample) %>%
      bind_rows(.)

    list(
      A = x$A[!is.na(x$A)],
      B = x$B[!is.na(x$B)],
      C = x$C[!is.na(x$C)]
    )
  }

  df %>%
    gather(key, prob) %>%
    rwebppl::get_samples(., num_samples = 100) %>%
    pull(key) %>%
    get_venn_samples() %>%
    ggVennDiagram(., label = NULL, color = 'black')+
    scale_fill_gradient(low = "white", high = "grey35",
                        limits = c(0, 100),
                        breaks = c(0, 50, 100),
                        labels = c(0, 0.5, 1),
                        name = "Probability")
}
```


# Figure 3

All As are Bs
All Bs are Cs

```{r}
# Regions that are compatible: 'ABC', 'ABC;BC', 'ABC;C', 'ABC;BC;C'.

all.all.1 <- data.frame(
  A = 0, B = 0, C = 0,
  AB = 0, BC = 0, AC = 0,
  ABC = 1
)

all.all.2 <- data.frame(
  A = 0, B = 0, C = 0,
  AB = 0, BC = 1, AC = 0,
  ABC = 1
)

all.all.3 <- data.frame(
  A = 0, B = 0, C = 1,
  AB = 0, BC = 0, AC = 0,
  ABC = 1
)

all.all.4 <- data.frame(
  A = 0, B = 0, C = 1,
  AB = 0, BC = 1, AC = 0,
  ABC = 1
)



aa1 <- venn_diagram_from_df(all.all.1) + guides(fill = F)
aa2 <- venn_diagram_from_df(all.all.2) + guides(fill = F)
aa3 <- venn_diagram_from_df(all.all.3) + guides(fill = F)
aa4 <- venn_diagram_from_df(all.all.4) + guides(fill = F)


plot_grid(aa1, aa2, aa3, aa4, ncol=4)
# ggsave("diagrams_allAB_allBC.pdf", width = 9, height = 2.25)
```


# Figure 4

All As are Bs
All Cs are Bs

[
  'ABC',       'AB;ABC',
  'ABC;BC',    'AB;BC',
  'AB;ABC;BC', 'ABC;B',
  'AB;ABC;B',  'ABC;B;BC',
  'AB;B;BC',   'AB;ABC;B;BC'
]

```{r}

all.all.3.1 <- data.frame(
  A = 0, B = 0, C = 0,
  AB = 0, BC = 0, AC = 0,
  ABC = 1
)

all.all.3.2 <- data.frame(
  A = 0, B = 0, C = 0,
  AB = 1, BC = 0, AC = 0,
  ABC = 1
)

all.all.3.3 <- data.frame(
  A = 0, B = 0, C = 0,
  AB = 0, BC = 1, AC = 0,
  ABC = 1
)

all.all.3.4 <- data.frame(
  A = 0, B = 0, C = 0,
  AB = 1, BC = 1, AC = 0,
  ABC = 0
)

all.all.3.5 <- data.frame(
  A = 0, B = 0, C = 0,
  AB = 1, BC = 1, AC = 0,
  ABC = 1
)

all.all.3.6 <- data.frame(
  A = 0, B = 1, C = 0,
  AB = 0, BC = 0, AC = 0,
  ABC = 1
)

all.all.3.7 <- data.frame(
  A = 0, B = 1, C = 0,
  AB = 1, BC = 0, AC = 0,
  ABC = 1)

all.all.3.8 <- data.frame(
  A = 0, B = 1, C = 0,
  AB = 0, BC = 1, AC = 0,
  ABC = 1)

all.all.3.9 <- data.frame(
  A = 0, B = 1, C = 0,
  AB = 1, BC = 1, AC = 0,
  ABC = 0
)

all.all.3.10 <- data.frame(
  A = 0, B = 1, C = 0,
  AB = 1, BC = 1, AC = 0,
  ABC = 1
)

aa21 <- venn_diagram_from_df(all.all.3.1) + guides(fill = F)
aa22 <- venn_diagram_from_df(all.all.3.2) + guides(fill = F)
aa23 <- venn_diagram_from_df(all.all.3.3) + guides(fill = F)
aa24 <- venn_diagram_from_df(all.all.3.4) + guides(fill = F)
aa25 <- venn_diagram_from_df(all.all.3.5) + guides(fill = F)
aa26 <- venn_diagram_from_df(all.all.3.6) + guides(fill = F)
aa27 <- venn_diagram_from_df(all.all.3.7) + guides(fill = F)
aa28 <- venn_diagram_from_df(all.all.3.8) + guides(fill = F)
aa29 <- venn_diagram_from_df(all.all.3.9) + guides(fill = F)
aa210 <- venn_diagram_from_df(all.all.3.10) + guides(fill = F)



plot_grid(aa21, aa22, aa23, aa24, aa25,
          aa26, aa27, aa28, aa29, aa210, ncol=5)

# ggsave("diagrams_allAB_allCB.pdf", width = 10, height = 4)

```


# Figure 5

```{r}
library(rwebppl)
get_samples_from_df = function(df, field1, field2){
  data.frame(df[[field1]][[field2]]) %>%
    pivot_longer(-probs, names_to = "key", values_to = "val") %>%
    group_by(key) %>%
    summarize(prob = sum(val * probs),
              utterance = field1,
              src = field2
              ) %>%
    rwebppl::get_samples(., num_samples = 1000)
}

wp.rs <- webppl(
  program_file = "syllogisms-r.wppl",
  data = c("M0_LIT"),
  data_var = "dataFromR",
  packages = c("./node_modules/vennUtils_oneShot")
)


wp.rs.samples <- bind_rows(
  map(names(wp.rs), function(s){
    map(names(wp.rs[[s]]), function(k){
      return(get_samples_from_df(wp.rs, s, k))
    })
  })
)


all_plots <- map(unique(wp.rs.samples$utterance),
                 function(x){ make_venn_digram (
                   wp.rs.samples %>% filter(src == "M0_LIT"), x
                   ) } )


cowplot::plot_grid(
  cowplot::plot_grid(
    all_plots[[1]] + theme(legend.position="none"),
    all_plots[[2]] + theme(legend.position="none"),
    all_plots[[3]] + theme(legend.position="none"), nrow = 1),
  legend,
  rel_widths = c(3, .4),
  nrow = 1,
  label_size = 12,
  labels = c(""),
  label_x = 0,
  hjust = -0.15
)

# ggsave("../publications/topics/figs/venn_literal_AA1_AI1_AA2_exp.pdf",
# width = 9, height = 3)
```

# Misc other diagrams


Data frames for Venn Diagrams

```{r}

empty.venn <- data.frame(
  A = 0, B = 0, C = 0,
  AB = 0, BC = 0, AC = 0,
  ABC = 0
)

barbara.venn <- data.frame(
  A = 0, B = 0, C = 1,
  AB = 1, BC = 1, AC = 0,
  ABC = 1
)

allsome.venn <- data.frame(
  A = 0, B = 1, C = 1,
  AB = 1, BC = 1, AC = 0,
  ABC = 0.5
)
```


# Visualizations

```{r}
plot1 <- venn_diagram_from_df(empty.venn) + guides(fill = F)
plot2 <- venn_diagram_from_df(barbara.venn) + guides(fill = F)
plot3 <- venn_diagram_from_df(allsome.venn) + guides(fill = F)

plot_grid(plot1, plot2, plot3, ncol=3,
          labels = c("i", "ii", "iii"))
```





No As are Bs
Some Bs are Cs

[
  'BC',       'AC;BC',
  'A;BC',     'A;AC;BC',
  'B;BC',     'B;AC;BC',
  'A;B;BC',   'A;B;AC;BC',

  'BC;C',     'AC;BC;C',
  'A;BC;C',   'A;AC;BC;C',
  'B;BC;C',   'B;AC;BC;C',
  'A;B;BC;C', 'A;B;AC;BC;C'
]

```{r}

none.some.1 <- data.frame(
  A = 0, B = 0, C = 0,
  AB = 0, BC = 1, AC = 0,
  ABC = 0
)

none.some.2 <- data.frame(
  A = 0, B = 0, C = 0,
  AB = 0, BC = 1, AC = 1,
  ABC = 0
)

none.some.3 <- data.frame(
  A = 1, B = 0, C = 0,
  AB = 0, BC = 1, AC = 1,
  ABC = 0
)

none.some.4 <- data.frame(
  A = 1, B = 0, C = 0,
  AB = 0, BC = 1, AC = 0,
  ABC = 0
)

none.some.5 <- data.frame(
  A = 0, B = 1, C = 0,
  AB = 0, BC = 1, AC = 0,
  ABC = 0
)

none.some.6 <- data.frame(
  A = 0, B = 1, C = 0,
  AB = 0, BC = 1, AC = 1,
  ABC = 0
)

none.some.7 <- data.frame(
  A = 1, B = 1, C = 0,
  AB = 0, BC = 1, AC = 0,
  ABC = 0
)

none.some.8 <- data.frame(
  A = 1, B = 1, C = 0,
  AB = 0, BC = 1, AC = 1,
  ABC = 0
)

none.some.9 <- data.frame(
  A = 0, B = 0, C = 1,
  AB = 0, BC = 1, AC = 0,
  ABC = 0
)

none.some.10 <- data.frame(
  A = 0, B = 0, C = 1,
  AB = 0, BC = 1, AC = 1,
  ABC = 0
)

none.some.11 <- data.frame(
  A = 1, B = 0, C = 1,
  AB = 0, BC = 1, AC = 1,
  ABC = 0
)

none.some.12 <- data.frame(
  A = 1, B = 0, C = 1,
  AB = 0, BC = 1, AC = 0,
  ABC = 0
)

none.some.13 <- data.frame(
  A = 0, B = 1, C = 1,
  AB = 0, BC = 1, AC = 0,
  ABC = 0
)

none.some.14 <- data.frame(
  A = 0, B = 1, C = 1,
  AB = 0, BC = 1, AC = 1,
  ABC = 0
)

none.some.15 <- data.frame(
  A = 1, B = 1, C = 1,
  AB = 0, BC = 1, AC = 0,
  ABC = 0
)

none.some.16 <- data.frame(
  A = 1, B = 1, C = 1,
  AB = 0, BC = 1, AC = 1,
  ABC = 0
)

ns1 <- venn_diagram_from_df(none.some.1) + guides(fill = F)
ns2 <- venn_diagram_from_df(none.some.2) + guides(fill = F)
ns3 <- venn_diagram_from_df(none.some.3) + guides(fill = F)
ns4 <- venn_diagram_from_df(none.some.4) + guides(fill = F)
ns5 <- venn_diagram_from_df(none.some.5) + guides(fill = F)
ns6 <- venn_diagram_from_df(none.some.6) + guides(fill = F)
ns7 <- venn_diagram_from_df(none.some.7) + guides(fill = F)
ns8 <- venn_diagram_from_df(none.some.8) + guides(fill = F)
ns9 <- venn_diagram_from_df(none.some.9) + guides(fill = F)
ns10 <- venn_diagram_from_df(none.some.10) + guides(fill = F)
ns11 <- venn_diagram_from_df(none.some.11) + guides(fill = F)
ns12 <- venn_diagram_from_df(none.some.12) + guides(fill = F)
ns13 <- venn_diagram_from_df(none.some.13) + guides(fill = F)
ns14 <- venn_diagram_from_df(none.some.14) + guides(fill = F)
ns15 <- venn_diagram_from_df(none.some.15) + guides(fill = F)
ns16 <- venn_diagram_from_df(none.some.16) + guides(fill = F)




plot_grid(ns1, ns2, ns3, ns4,
          ns5, ns6, ns7, ns8,
          ns9, ns10, ns11, ns12,
          ns13, ns14, ns15, ns16, ncol=4)

# ggsave("diagrams_noneAB_someBC.pdf", width = 9, height = 7)

```

No As are Bs
No Bs are Cs

[
  '',       'AC',
  'A',     'A;AC',
  'B',     'B;AC',
  'A;B',   'A;B;AC',

  'C',     'AC;C',
  'A;C',   'A;AC;C',
  'B;C',   'B;AC;C',
  'A;B;C', 'A;B;AC;C'
]

       C     B    BC     A    AC    AB   ABC
1  FALSE FALSE FALSE FALSE FALSE FALSE FALSE
2  FALSE FALSE FALSE FALSE  TRUE FALSE FALSE
3  FALSE FALSE FALSE  TRUE FALSE FALSE FALSE
4  FALSE FALSE FALSE  TRUE  TRUE FALSE FALSE
5  FALSE  TRUE FALSE FALSE FALSE FALSE FALSE
6  FALSE  TRUE FALSE FALSE  TRUE FALSE FALSE
7  FALSE  TRUE FALSE  TRUE FALSE FALSE FALSE
8  FALSE  TRUE FALSE  TRUE  TRUE FALSE FALSE
9   TRUE FALSE FALSE FALSE FALSE FALSE FALSE
10  TRUE FALSE FALSE FALSE  TRUE FALSE FALSE
11  TRUE FALSE FALSE  TRUE FALSE FALSE FALSE
12  TRUE FALSE FALSE  TRUE  TRUE FALSE FALSE
13  TRUE  TRUE FALSE FALSE FALSE FALSE FALSE
14  TRUE  TRUE FALSE FALSE  TRUE FALSE FALSE
15  TRUE  TRUE FALSE  TRUE FALSE FALSE FALSE
16  TRUE  TRUE FALSE  TRUE  TRUE FALSE FALSE


```{r}

none.none.1 <- data.frame(
  A = 0, B = 0, C = 0,
  AB = 0, BC = 0, AC = 0,
  ABC = 0
)

none.none.2 <- data.frame(
  A = 0, B = 0, C = 0,
  AB = 0, BC = 0, AC = 1,
  ABC = 0
)

none.none.3 <- data.frame(
  A = 1, B = 0, C = 0,
  AB = 0, BC = 0, AC = 1,
  ABC = 0
)

none.none.4 <- data.frame(
  A = 1, B = 0, C = 0,
  AB = 0, BC = 0, AC = 0,
  ABC = 0
)

none.none.5 <- data.frame(
  A = 0, B = 1, C = 0,
  AB = 0, BC = 0, AC = 0,
  ABC = 0
)

none.none.6 <- data.frame(
  A = 0, B = 1, C = 0,
  AB = 0, BC = 0, AC = 1,
  ABC = 0
)

none.none.7 <- data.frame(
  A = 1, B = 1, C = 0,
  AB = 0, BC = 0, AC = 0,
  ABC = 0
)

none.none.8 <- data.frame(
  A = 1, B = 1, C = 0,
  AB = 0, BC = 0, AC = 1,
  ABC = 0
)

none.none.9 <- data.frame(
  A = 0, B = 0, C = 1,
  AB = 0, BC = 0, AC = 0,
  ABC = 0
)

none.none.10 <- data.frame(
  A = 0, B = 0, C = 1,
  AB = 0, BC = 0, AC = 1,
  ABC = 0
)

none.none.11 <- data.frame(
  A = 1, B = 0, C = 1,
  AB = 0, BC = 0, AC = 1,
  ABC = 0
)

none.none.12 <- data.frame(
  A = 1, B = 0, C = 1,
  AB = 0, BC = 0, AC = 0,
  ABC = 0
)

none.none.13 <- data.frame(
  A = 0, B = 1, C = 1,
  AB = 0, BC = 0, AC = 0,
  ABC = 0
)

none.none.14 <- data.frame(
  A = 0, B = 1, C = 1,
  AB = 0, BC = 0, AC = 1,
  ABC = 0
)

none.none.15 <- data.frame(
  A = 1, B = 1, C = 1,
  AB = 0, BC = 0, AC = 0,
  ABC = 0
)

none.none.16 <- data.frame(
  A = 1, B = 1, C = 1,
  AB = 0, BC = 0, AC = 1,
  ABC = 0
)

ns1 <- venn_diagram_from_df(none.none.1) + guides(fill = F)
ns2 <- venn_diagram_from_df(none.none.2) + guides(fill = F)
ns3 <- venn_diagram_from_df(none.none.3) + guides(fill = F)
ns4 <- venn_diagram_from_df(none.none.4) + guides(fill = F)
ns5 <- venn_diagram_from_df(none.none.5) + guides(fill = F)
ns6 <- venn_diagram_from_df(none.none.6) + guides(fill = F)
ns7 <- venn_diagram_from_df(none.none.7) + guides(fill = F)
ns8 <- venn_diagram_from_df(none.none.8) + guides(fill = F)
ns9 <- venn_diagram_from_df(none.none.9) + guides(fill = F)
ns10 <- venn_diagram_from_df(none.none.10) + guides(fill = F)
ns11 <- venn_diagram_from_df(none.none.11) + guides(fill = F)
ns12 <- venn_diagram_from_df(none.none.12) + guides(fill = F)
ns13 <- venn_diagram_from_df(none.none.13) + guides(fill = F)
ns14 <- venn_diagram_from_df(none.none.14) + guides(fill = F)
ns15 <- venn_diagram_from_df(none.none.15) + guides(fill = F)
ns16 <- venn_diagram_from_df(none.none.16) + guides(fill = F)




plot_grid(ns1, ns2, ns3, ns4,
          ns5, ns6, ns7, ns8,
          ns9, ns10, ns11, ns12,
          ns13, ns14, ns15, ns16, ncol=4)

ggsave("diagrams_noneAB_noneBC.pdf", width = 9, height = 7)

```
